Motif roles provides unique information about species risk of extinction\\ \medskip Supplementary Information

### 2022-06-14 manuscript/supplement_motifs.tex
reordered SI
converted all figs to eps

@@

\section{Calculating persistence}

@@

    \begin{figure}[hb!]
     \centering
     \includegraphics[width=.9\textwidth]{figures/heatmap_STL_allCS_BP0.pdf}
     \caption{All species across all levels experience a risk of going extinct due to causes not related to the web of $\pi = 0.1$. The sub figures show final persistence for consumers with different shortest trophic length, for increasing connectance (y-axis) and network size (x-axis). Persistence decreases with darker color in the heat map.}
     \label{fig:heatmap_stl_BP0}
    \end{figure}

    \begin{figure}[hb!]
     \centering
     \includegraphics[width=.9\textwidth]{figures/heatmap_STL_allCS_BP1.pdf}
     \caption{Basal resources experience a disturbance increasing their probability to go extinct to $\pi = 0.5$. All consumer species go extinct due to causes not related to the web itself with probability $\pi = 0.1$. The sub figures show final persistence for consumers with different shortest trophic length, for increasing connectance (y-axis) and network size (x-axis). Persistence decreases with darker color in the heat map.}
     \label{fig:heatmap_stl_BP1}
    \end{figure}

@@

    \begin{figure}[hb!]
        \centering
            \includegraphics[width=\textwidth]{figures/prop_dens_bp_vs_S_allC.pdf}
            \caption{Here we show the density (y-axis) of slopes (x-axis) of persistence against proportion of different motifs for all simulated webs of all connectances - a visualization of how an increased proportion of each motif (different colored lines) affects persistence of consumer species. Columns show the result for various disturbances on the basal level, from $\pi = 0.1$ (left) to $\pi = 0.5$ (right). Rows show various network sizes. The dotted, vertical lines indicate zero on the x-axis. A negative slope value reflects a negative relationship between increased participation in a motif and persistence, while a positive slope value reflects a positive relationship - an increased proportion of a specific motif increase persistence. The fraction of replicates with a slope greater than zero are stated in numbers in each sub-plot, the color corresponding to each motif (legend). }
            \label{fig:density_prop_S}
        \end{figure}

>>>>

\linenumbers
\section{Calculating persistence}

@@

@@

    \begin{figure}[hb!]
     \centering
     \includegraphics[width=.9\textwidth]{figures/heatmap_STL_allCS_BP0.eps}
     \caption{All species across all levels experience a risk of going extinct due to causes not related to the web of $\pi = 0.1$. The sub figures show final persistence for consumers with different shortest trophic length, for increasing connectance (y-axis) and network size (x-axis). Persistence decreases with darker color in the heat map.}
     \label{fig:heatmap_stl_BP0}
    \end{figure}

    \begin{figure}[hb!]
     \centering
     \includegraphics[width=.9\textwidth]{figures/heatmap_STL_allCS_BP1.eps}
     \caption{Basal resources experience a disturbance increasing their probability to go extinct to $\pi = 0.5$. All consumer species go extinct due to causes not related to the web itself with probability $\pi = 0.1$. The sub figures show final persistence for consumers with different shortest trophic length, for increasing connectance (y-axis) and network size (x-axis). Persistence decreases with darker color in the heat map.}
     \label{fig:heatmap_stl_BP1}
    \end{figure}

@@

    \begin{figure}[hb!]
        \centering
            \includegraphics[width=\textwidth]{figures/prop_dens_bp_vs_S_allC.eps}
            \caption{Here we show the density (y-axis) of slopes (x-axis) of persistence against proportion of different motifs for all simulated webs of all connectances - a visualization of how an increased proportion of each motif (different colored lines) affects persistence of consumer species. Columns show the result for various disturbances on the basal level, from $\pi = 0.1$ (left) to $\pi = 0.5$ (right). Rows show various network sizes. The dotted, vertical lines indicate zero on the x-axis. A negative slope value reflects a negative relationship between increased participation in a motif and persistence, while a positive slope value reflects a positive relationship - an increased proportion of a specific motif increase persistence. The fraction of replicates with a slope greater than zero are stated in numbers in each sub-plot, the color corresponding to each motif (legend). }
            \label{fig:density_prop_S}
        \end{figure}
